comgen-outline

### 2017-06-09 paper/appendix-cueValidity.Rmd
create alt models appendix; begin full posterior appendix
fix path in appendices

```{r echo = F}
library(langcog)
library(tidyverse)
library(ggthemes)
library(jsonlite)
theme_set(theme_few())
project.path <- "~/Documents/research/communicating-generalizations/"
data.path <- "data/generics/endorsement/"
substrRight <- function(x, n){
  substr(x, nchar(x)-n+1, nchar(x))
}
```

@@

In considering generalizations about categories, or *generic language*, theories try to formalize the truth conditions by analogy to quantified statements (e.g., *some*, *most*, ...).
Here, the prevalence of the feature, or $P(f \mid k)$, is the important quantity.
Quantifiers can be described as conditions on prevalence: $\denote{some} = \{P(f \mid k) > 0\}, \denote{most} = \{P(f \mid k) > 0.5\}, \denote{all} = \{P(f \mid k) = 1\}$.
The question for formal semantic theories has been: is there some threshold $\theta$ beyond which generic statements become true?
Hard-constraints on $\theta$ are difficult to defend because of cases like *Mosquitos carry malaria*, where only the weakest threshold would suffice.

>>>>

```{r echo = F}
library(langcog)
library(tidyverse)
library(ggthemes)
library(jsonlite)
theme_set(theme_few())
project.path <- "../"
data.path <- "data/generics/endorsement/"
substrRight <- function(x, n){
  substr(x, nchar(x)-n+1, nchar(x))
}
```

@@

In considering generalizations about categories, or *generic language*, theories try to formalize the truth conditions by analogy to quantified statements (e.g., *some*, *most*, ...).
Here, the prevalence of the feature, or $P(f \mid k)$, is the central quantity.
Quantifiers can be described as conditions on prevalence: $\denote{some} = \{P(f \mid k) > 0\}, \denote{most} = \{P(f \mid k) > 0.5\}, \denote{all} = \{P(f \mid k) = 1\}$.
The question for formal semantic theories has been: is there some threshold $\theta$ beyond which generic statements become true?
Hard-constraints on $\theta$ are difficult to defend because of cases like *Mosquitos carry malaria*, where only the weakest threshold would suffice.

### 2017-06-09 paper/appendix-fullModelPosteriors.Rmd
fix path in appendices

```{r libraries}
library(rwebppl)
library(xtable)
library(tidyverse)
library(forcats)
library(langcog)
library(data.table)
library(coda)
library(ggthemes)
library(ggrepel)
library(jsonlite)
theme_set(theme_few())
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
project.path <- "~/Documents/research/comgen-paper/"
data.path <- "data/generics/endorsement/"
model.path <- "models/generics/results/"
options("scipen"=10) 
```

>>>>

```{r libraries}
library(rwebppl)
library(xtable)
library(tidyverse)
library(forcats)
library(langcog)
library(data.table)
library(coda)
library(ggthemes)
library(ggrepel)
library(jsonlite)
theme_set(theme_few())
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
project.path <- "../"
data.path <- "data/generics/endorsement/"
model.path <- "models/generics/results/"
options("scipen"=10) 
```
